Upgrades to the SINQ Cold Neutron Source

### 2015-09-08 paper.tex
adding results

plot of spectral band, FOM is

@@

plot of geometry in XY

>>>>

With all of the variance reduciton and approximations implmented, each case takes about one hours to run.  The spectra from all the casesa are shown in upper plot in Figure \ref{parametric_REH}, and the figure of merit of each case is shown in the lower plot.  The figure of merit was simply chosen to be the total current exiting the guide from 3 to 6 \AA.  The perfomance is

@@

The geometry of the best-performing case is shown in figure \ref{case077}.
